A survey of HTTP caching options on the open Web

### 2014-12-18 sanity/paper1.tex
fix appendices more reorg
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@912 43ef1190-90fd-4dd7-a769-d0121f02b80e

%\documentclass{llncs}
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}
%\usepackage{wrapfig}

@@

\section{Implementation}

@@

\section{Implementation details\todo{proper formatting}}\label{app:reduction}

@@

We then developed a fairly elaborate parallel spider to get the
resources found on 3117 unique hosts in the previous steps using the
Perl frameworks RDF::Trine and libwww. The spider operated with a
timeout of 20 seconds and a maximum message size it would accept of 1
MB.

@@

Finally, if the LOV SPARQL endpoint used a URI for the vocabulary that
was different from the namespace URI (after a normalization step),
another request would be made to record the selected HTTP headers from
that as well.

>>>>

%\documentclass{llncs}
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}
%\usepackage{wrapfig}
\usepackage{appendix}

@@

\section{Methodology}

@@

The end result of this process is a list of 3117 unique hosts, for
each several resources would be visited, some several times, as they
may host SPARQL Endpoints, ontologies, or other information resources,
by a spider detailed in Appendix~\ref{app:fetcher}

This results in an NQuads file per host, which is then loaded into a
SPARQL Endpoint\todo{which} for analysis by using the statistics
system R.

\begin{appendices}

\section{Implementation of data reduction}\label{app:reduction}

@@

\section{Implementation of spider}\label{app:fetcher}

We then developed a fairly elaborate parallel spider to examine the
resources found on hosts that the previous steps deemed interesting
using the Perl frameworks RDF::Trine and libwww. The spider operated
with a timeout of 20 seconds and a maximum message size it would
accept of 1 MB.

@@

Finally, if the LOV SPARQL endpoint used a URI for the vocabulary that
was different from the namespace URI (after a normalization step),
another request would be made to record the selected HTTP headers from
that as well.
\end{appendices}
